Modular Inverse Reinforcement Learning on Human Motion

### 2015-02-11 paper.tex
fixed easy part first

\begin{figure}[h!]
\centering
\includegraphics[height=6cm]{human.jpg}
\includegraphics[height=6cm]{env.png}
\caption{(Left) A volunteer with head tracker, virtual reality displayer, and
body tracker.  (Right) The environment the human can see through the displayer.}
\label{fig:avatar}
\end{figure}

%FIXME
In Figure~\ref{fig:avatar} shows the domain that we use in this paper. The red
cubes represent obstacles, that the player would be punished if running
into. The blue balls represent targets, that the player would be rewarded if
collected. There is also a gray path on the ground that the player can follow.
Naturally, this domain has three subtasks, 1) following the path, 2)
collecting targets, 3) avoiding obstacles.
This is an experiment used in the
literature to evaluate modular reinforcement learning
\cite{rothkopf2013modular}.
We ask our volunteers to have trackers and virtual reality displayers equipped. He
can see the envrionment through the displayer in front of his eyes. So he can
walk as if he is walking in the virtual domain.

We will evaluate four different tasks. {\bf Task 1}, following the path only, and
ignoring other objects. {\bf Task 2}, following the path, while avoid the obstacles.
{\bf Task 3}, following the path, while attain targets when possible. {\bf Task 4},
following the path, collecting the targets and avoiding obstacles
simultaneously.
We conducted experiments to ask volunteers to accomplish different tasks and
recorded their trajectories. The human data are collected by the Center for
Perceptual Systems at University of Texas at Austin.

If the player observes the distance and angle to an object, he is expected to
know the optimal action to avoid or pursue it. This decision is also Markov.
Therefore, the question would be, if we have trained modules for these three
subtasks, could they be integrated to match human's behavior?

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.24\textwidth]{task_1.png}
\includegraphics[width=0.24\textwidth]{task_2.png}
\includegraphics[width=0.24\textwidth]{task_3.png}
\includegraphics[width=0.24\textwidth]{task_4.png}
\caption{The trajectories of humans and our agent in four different tasks. From
left to right are Task 1 to Task 4. The active modules should be (Path),
(Obstacle + Path), (Target + Path), (Target + Obstacle + Path), respectively.}
\label{fig:exp}
\end{figure}

\begin{table}[h!]
\centering
\begin{tabular}{| l| l| l |}
\hline
Average by Task & Num Targs Hit & Num Obst Hit\\
\hline
1 & 2.34 &  2.13\\
\hline
2 & 3.03 &  \bf{0.13}\\
\hline
3 & \bf{10.19} & 2.28\\
\hline
4 & \bf{9.88} &  \bf{0.03}\\
\hline
\end{tabular}
\caption{Number of targets hit and number of obstacles hit of the humans.}
\label{tb:human}
\end{table}

\begin{table}[h!]
\centering
\begin{tabular}{| l| l| l |}
\hline
Average by Task & Num Targs Hit & Num Obst Hit\\
\hline
1 & 1.25 & 1.62\\
\hline
2 & 3.62 & \bf{2.37}\\
\hline
3 & \bf{5.14} & 3.14\\
\hline
4 & \bf{5.00} & \bf{2.00}\\
\hline
\end{tabular}
\caption{Number of targets hit and number of obstacles hit of the learning agent.}
\label{tb:agent}
\end{table}

We report the results in Figure~\ref{fig:exp}, same as Figure~\ref{fig:avatar},
the red circles are obstacles. The blue circles are targets. The gray lines are
the path. The black lines are trajectories of human --- each line represents one
human trajectory.
Using the weights derived from the algorithm, the trajectories of our agents are
drawn in green color.

Although humans don't agree each other on how to avoid obstacles or collecting
targets, our agent can figure out what the humans are doing, and perform a
similar trajectory. Table~\ref{tb:human} and Table~\ref{tb:agent} evaluate the
performance by showing the number of targets hit and number of obstacles hit.
Note that the numbers bold-ed are active modules in the corresponding task. We
can observe that humans still do better than our agent in these tasks.

@@

We interpreted human behavior using inverse module reinforcement learning in
this paper. We have some positive results, but the performance of our agent is
still inferior than humans.

>>>>

\begin{figure}[h!]
\centering
\includegraphics[height=5cm]{human.jpg}
\includegraphics[height=5cm]{env.png}
\caption{(Left) A human subject with head tracker, virtual reality displayer, and
body tracker.  (Right) The environment the human can see through the displayer.}
\label{fig:avatar}
\end{figure}

%FIXME
In Figure~\ref{fig:avatar} shows the domain that we use in this paper. The red
cubes represent obstacles, that the agent would be punished if running
into. The blue balls represent targets, that the agent would be rewarded if
collected. There is also a gray path on the ground that the agent can follow.
Naturally, this domain has three subtasks, 1) following the path, 2)
collecting targets, 3) avoiding obstacles.
This is an experiment used in the
literature to evaluate modular reinforcement learning
\cite{rothkopf2013modular}.
We ask human subjects to have trackers and virtual reality displayers equipped. He
can see the envrionment through the displayer in front of his eyes. So he can
walk as if he is walking in the virtual domain.

We will evaluate four different tasks. {\bf Task 1}, following the path only, and
ignoring other objects. {\bf Task 2}, following the path, while avoid the obstacles.
{\bf Task 3}, following the path, while attain targets when possible. {\bf Task 4},
following the path, collecting the targets and avoiding obstacles
simultaneously.
We conducted experiments to ask human subjects to accomplish different tasks and
recorded their trajectories. The human data are collected by the Center for
Perceptual Systems at University of Texas at Austin.

If the agent observes the distance and angle to an object, he is expected to
know the optimal action to avoid or pursue it. This decision is also Markov.
Therefore, the question would be, if we have trained modules for these three
subtasks, could they be integrated to match human's behavior?

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.24\textwidth]{task_1.png}
\includegraphics[width=0.24\textwidth]{task_2.png}
\includegraphics[width=0.24\textwidth]{task_3.png}
\includegraphics[width=0.24\textwidth]{task_4.png}
\caption{The trajectories of humans and the agent in four different tasks. (Path),
(Obstacle + Path), (Target + Path), (Target + Obstacle + Path), respectively.}
\label{fig:exp}
\end{figure}

We report the results in Figure~\ref{fig:exp}, same as Figure~\ref{fig:avatar},
the red circles are obstacles. The blue circles are targets. The gray lines are
the path. The black lines are trajectories of human --- each line represents one
human trajectory.
Using the weights derived from the algorithm, the trajectories of the agents are
drawn in green color.

\begin{figure}[h!]
\centering
\includegraphics[width=0.6\textwidth]{contactStats.png}
\caption{Number of targets hit and number of obstacles hit of the human subjects
and the agent.}
\label{fig:heatmap}
\end{figure}

Although humans don't agree each other on how to avoid obstacles or collecting
targets, the agent can figure out what the humans are doing, and perform a
similar trajectory. Table~\ref{tb:human} and Table~\ref{tb:agent} evaluate the
performance by showing the number of targets hit and number of obstacles hit.
Note that the numbers bold-ed are active modules in the corresponding task. We
can observe that humans still do better than the agent in these tasks.

@@

We interpreted human behavior using inverse module reinforcement learning in
this paper. We have some positive results, but the performance of the agent is
still inferior than humans.
